---
title: "r-week-8-hw-eeb177"
output: html_document
---
#1. Canids Continued
```{r}
setwd("~/Desktop/eeb-177/homework")
canids <- read.csv("canids-ranges.csv", header = F, as.is = T)
names(canids) <- c("genus", "species", "minage", "maxage")
head(canids)

canid_occ <- ggplot(canids, aes( species, ymin = maxage, ymax=minage, colour = genus))
canid_occ <- canid_occ + geom_linerange()
canid_occ

canid_occ <- canid_occ + theme(legend.position="none")
canid_occ

canid_occ <- canid_occ + coord_flip()
canid_occ

canid_occ <- canid_occ +  theme(axis.text.y = element_text(size=3))
canid_occ

canid_occ <- canid_occ + labs(title = "Canid Fossil Occurrences", x = "Species", y = "Ma ago") + theme(plot.title = element_text(hjust = 0.5, size=22, face = "bold"), axis.title =element_text(size=20))
canid_occ
```

#Answering question. First.
#1. What taxonomic group is displayed? 
  
    canids
#2. How many unique fossil species are contained within it?
   #length(canids$species)
   
171

#3. How many unique fossil genera?
   #nrow(canids[!duplicated(canids$genus), ])
58


#4. What species has the longest
Cormocyon,Cormocyon copei


#Answering question. Second part with Blattodea data file.
```{r}
library(ggplot2)
setwd("~/Desktop/eeb-177/homework") 
Blattodea <- read.csv("Blattodea-ranges.csv", header = F, as.is = T)
names(Blattodea) <- c("genus", "species", "minage", "maxage")
head(Blattodea)

Blattodea_occ <- ggplot(Blattodea, aes( species, ymin = maxage, ymax=minage, colour = genus))
Blattodea_occ <- Blattodea_occ + geom_linerange()
Blattodea_occ

Blattodea_occ <- Blattodea_occ + theme(legend.position="none")
Blattodea_occ
Blattodea_occ <- Blattodea_occ + coord_flip()
Blattodea_occ

Blattodea_occ <- Blattodea_occ + labs(title = "Canid Fossil Occurrences", x = "Species", y = "Ma ago") + theme(plot.title = element_text(hjust = 0.5, size=22, face = "bold"), axis.title =element_text(size=20))
Blattodea_occ
```

#1. What taxonomic group is displayed? 
      Blattodea.
#2. How many unique fossil species are contained within it?
      1430
#3. How many unique fossil genera?
      490
#4. What species has the longest
    Blattodea




#Part 2. Data Frames
#Exploring Data frames
#1
```{r}
df <- data.frame(first = c('Jung'),
                 last = c('Kim'),
                 lucky_number = c(4),
                 stringsAsFactors = FALSE)
df <- rbind(df, list('Joe', 'Bruin', 7) )
df <- cbind(df, coffeetime = c(TRUE,FALSE))
df
```

#2
```{r}
download.file("https://raw.githubusercontent.com/swcarpentry/r-novice-gapminder/gh-pages/_episodes_rmd/data/gapminder-FiveYearData.csv", destfile = "data/gapminder-FiveYearData.csv")
gapminder <- read.csv(file = "data/gapminder-FiveYearData.csv")

source(file = "scripts/load-gapminder.R")
```

#3
```{r}
The object gapminder is a data frame with columns

    country and continent are factors.
    year is an integer vector.
    pop, lifeExp, and gdpPercap are numeric vectors.

```


#Subsetting Data.
#1.
```{r}
x <- c(5.4, 6.2, 7.1, 4.8, 7.5)
names(x) <- c('a', 'b', 'c', 'd', 'e')
x<- x[-c(1,5)]
print(x)
```

#2
```{r}
x <- c(5.4, 6.2, 7.1, 4.8, 7.5)
names(x) <- c('a', 'b', 'c', 'd', 'e')
print(x)
x[-which(names(x) == "g")]
#answer is A) if there are no TRUE values passed to which, an empty vector is returned and C) integer() is an empty vector.
```

#3
```{r}
x <- c(5.4, 6.2, 7.1, 4.8, 7.5)
names(x) <- c('a', 'b', 'c', 'd', 'e')
print(x)

subsetting <- x[x<7 & x >4]

print(subsetting)

```

#4
```{r}
m <- matrix(1:18, nrow=3, ncol=6)
m[2,c(4,5)]

# Answer:D. m[2,c(4,5)]
```

#5
```{r}
xlist <- list(a = "Software Carpentry", b = 1:10, data = head(iris))
xlist$b[2]
```

#6
```{r}
mod <- aov(pop ~ lifeExp, data=gapminder)
attributes(mod) ## `df.residual` is one of the names of `mod`
mod$df.residual
```

#7
```{r}
#1)gapminder[gapminder$year == 1957,]

#2)gapminder[,-c(1:4)]

#3)gapminder[gapminder$lifeExp > 80,]

#4)gapminder[1, c(4, 5)]

#5)gapminder[gapminder$year == 2002 | gapminder$year == 2007,] #gapminder[gapminder$year %in% c(2002, 2007),]
```

#8
```{r}
#1. gapminder is a data.frame so needs to be subsetted on two dimensions. gapminder[1:20, ] subsets the data to give the first 20 rows and all columns.
#2. gapminder_small <- gapminder[c(1:9, 19:23),]
```

#Creating Publication-Quality Graphics

#1
```{r}
gapminder <- read.csv("gapminder-FiveYearData.csv")
#ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) + geom_point()
ggplot(data = gapminder, aes(x = year, y = lifeExp)) + geom_point()
```

#2
```{r}
gapminder <- read.csv("gapminder-FiveYearData.csv")
ggplot(data = gapminder, aes(x = year, y = lifeExp, color=continent)) +
  geom_point()
```

#3
```{r}
ggplot(data = gapminder, aes(x=year, y=lifeExp, by=country)) +
 geom_point() + geom_line(aes(color=continent))
```

#4
```{r}
#4a.
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) +
 geom_point(size=3, color="orange") + scale_x_log10() +
 geom_smooth(method="lm", size=1.5)

#4b.
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp, color = continent)) +
geom_point(size=3, pch=17) + scale_x_log10() +
geom_smooth(method="lm", size=1.5)
```

#5
```{r}
ggplot(data = gapminder, aes(x = gdpPercap, fill=continent)) +
 geom_density(alpha=0.6) + facet_wrap( ~ year) + scale_x_log10()
```